Predicting computational reproducibility of data analysis pipelines \\in large population studies using collaborative filtering

### 2018-07-30 paper.tex
Added overlap FS matrix

@@

\todo{Discussion on points that are not part of constant lines. Soudabeh: add an overlap matrix for FS, RFNU, ALS, at 0.5 or 0.6.}

\todo{Make sure the code is available and results are reproducible. Soudabeh: push your code to reprotools. Tristan: release and check.}

>>>>

Figure~\ref{fig:error-locality} shows the results obtained by RFNU on 
the Freesurfer dataset for a training ratio of 0.6. The prediction 
error is localized (1) at the bottom of the matrix, which corresponds 
to the end of the execution, and (2) in the regions where file 
reproducibility varies across subjects, i.e., lines are not entirely 
black or entirely white.
\begin{figure}
\includegraphics[width=0.6\columnwidth]{figures/RFNU_FS100F_ALS_06_test_data_matrix_run1.png}
\caption{Prediction results for RFNU on the Freesurfer dataset, $\alpha=0.6$.}
\label{fig:error-locality}
\end{figure}

@@

The code and data used in this paper are available at 
\url{https://github.com/big-data-lab-team/paper-reproducibility-collaborative-filtering}.

\todo{Soudabeh: push your code to reprotools. Tristan: release and check.}
